The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-02-24 paper.tex
add images of the smeared visibilities to illustrate the RFI

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{plots/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO LWA.
        The 200 meter diameter area indicated by the dashed line contains 251 antennas distributed
        in a pseudo-random configuration. The 32 filled circles are the expansion antennas built in
        early 2016 to increase the longest baseline to 1.5 km. The 5 open circles are antennas
        equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

@@

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{figures/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO LWA.
        The 200 meter diameter area indicated by the dashed line contains 251 antennas distributed
        in a pseudo-random configuration. The 32 filled circles are the expansion antennas built in
        early 2016 to increase the longest baseline to 1.5 km. The 5 open circles are antennas
        equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

@@

\begin{figure*}[ht]
    \centering
    \begin{tabular}{cccc}
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
    \end{tabular}
    \caption{
        Snapshot images after smearing the visiblities over the entire 100 hour observation window.
    }
\end{figure*}
